\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-15 experience.tex
save one line space

@@

>>>>

- \psharp generalized beyond vNext. \psharp is not only applicable to vNext but in many systems.
- Advanced safety properties
- Handles intra-machine concurrency
- Writing the protocol while testing it (co-development)

@@

- \psharp generalized beyond vNext. \psharp is not only applicable to vNext but in many systems.
- (Advanced) safety properties?
- What we developed is a model that other people can reuse. Plugin the model and test the user application.
- Example of advanced modeling capability of \psharp. One component talks to another sophisticated API. We demonstrate environmental modeling expressivity in system engineering.

### 2015-09-15 paper.tex
save one line space

%for single author (just remove % characters)
\author{
{\rm Pantazis Deligiannis$^\dagger$, Matt McCutchen$^\diamond$, Paul Thomson$^\dagger$, Shuo Chen$^\star$}\\
{\rm Alastair F. Donaldson$^\dagger$, John Erickson$^\star$, Cheng Huang$^\star$, Akash Lal$^\star$}\\
{\rm Rashmi Mudduluru$^\star$, Shaz Qadeer$^\star$, Wolfram Schulte$^\star$}\\\\
$^\dagger$Imperial College London, $^\star$Microsoft\\
$^\diamond$Massachusetts Institute of Technology\\
} % end author

>>>>

%for single author (just remove % characters)
\author{
{\rm Pantazis Deligiannis$^\dagger$, Matt McCutchen$^\diamond$, Paul Thomson$^\dagger$, Shuo Chen$^\star$}\\
{\rm Alastair F. Donaldson$^\dagger$, John Erickson$^\star$, Cheng Huang$^\star$, Akash Lal$^\star$}\\
{\rm Rashmi Mudduluru$^\star$, Shaz Qadeer$^\star$, Wolfram Schulte$^\star$}\\\\
$^\dagger$Imperial College London, $^\star$Microsoft, $^\diamond$Massachusetts Institute of Technology\\
} % end author
